\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-11-27 Final Paper/PaperJLin.tex
Added minor edits

	\e{Hypothesis 3D -- Polity Differences} The regime's level of democracy, age and electoral formula will cooperate to determine the extent to which place of residence can influence political ideology in a given polity.
\end{quote}

>>>>

	\e{Hypothesis 3D -- Polity Differences:} The regime's level of democracy, age and electoral formula will cooperate to determine the extent to which place of residence can influence political ideology in a given polity.
\end{quote}
